Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-01 ProbabilisticCoherence.tex
Discussion of why MinT works added

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
%\end{equation}
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
\subsection{Elliptical Distributions}
We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.  Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions. 
\begin{theo}[Reconciliation for Elliptical Distributions]
	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.  Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.  Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is the true variance covariance matrix of the predictive distribution for the bottom level. 
\end{theo}
\begin{proof}
   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).  The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.  The reconciled scale matrix is 
   \begin{align*}
   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm A}{\bm\Sigma}^{-1/2}{\bm \Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm A}'{\bm S}'\\
   =&{\bm S}{\bm \Omega}{\bm S}'\\
   =&{\bm \Sigma}
   \end{align*}
   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location vector is 
   \begin{align*}
   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}\\
   =&{\bm \mu}\\
   \end{align*}
\end{proof}	
A number of insights can be drawn from this theorem.  First, although a linear mapping $g(.)$ can be used to recover the true density in the elliptical case, the same does not hold in general.  Second, $g(.)$ is not, in general, a projection matrix.  Third, ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.

\todo{Some discussion about why projections are good}.

>>>>

%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
%\begin{equation}\label{eq:gaussianreconciled}
%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
%\end{equation}
Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.  The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
\subsection{Elliptical Distributions}
We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.  Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions. 
\begin{theo}[Reconciliation for Elliptical Distributions]
	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.  Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.  Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is the true variance covariance matrix of the predictive distribution for the bottom level. 
\end{theo}
\begin{proof}
   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).  The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.  The reconciled scale matrix is 
   \begin{align*}
   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm A}{\bm\Sigma}^{-1/2}{\bm \Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm A}'{\bm S}'\\
   =&{\bm S}{\bm \Omega}{\bm S}'\\
   =&{\bm \Sigma}
   \end{align*}
   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location vector is 
   \begin{align*}
   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}\\
   =&{\bm \mu}\\
   \end{align*}
\end{proof}	
A number of insights can be drawn from this theorem.  First, although a linear mapping $g(.)$ can be used to recover the true density in the elliptical case, the same does not hold in general.  Second, $g(.)$ is not, in general, a projection matrix.  The conditions for which a the true predictive density can be recovered by reconciliation are given below.

\begin{theo}[True predictive via projection]
	Assume that the true predictive distribution is elliptical with location ${\bm mu}$ and scale ${\bm Sigma}$.  Consider reconciliation via a projection $g({\bm y})=({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm y}$
	The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm \mu}$ $\hat{\bm \Sigma}$ and scale when the following conditions hold.
	\begin{align}
	sp(\hat{\bm\mu}-{\bm \mu})&\subset sp(\bm{R})\\
    sp(\bm{\Sigma}^{1/2}-{\bm \Sigma}^{1/2})&\subset sp({\bm R})\\
	\end{align}
\end{theo}
\begin{proof}
	The reconciled location vector will be given by
	\begin{align*}
		\tilde{\bm \mu}&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\hat{\bm \mu}\\
		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}+{\bm \mu}-{\bm \mu}\right)\\
		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm \mu}+{\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}-{\bm \mu}\right)\\
	\end{align*}
  Since ${\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and ${\bm \mu}\in\mathfrak{s}$ the first term simplified to ${\bm \mu}$.  If ${\bm \mu}-\hat{\bm \mu}$ lies in the span of ${\bm R}$ then multiplication by ${\bm R}'_{\perp}$ reduced the second term to ${\bm 0}$.  By a similar argument it can be shown that $\tilde{\bm \Sigma}^{1/2}={\bm \Sigma}^{1/2}$.  The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
\end{proof}  
Although these conditions will rarely hold in practice and only apply to a limited class of distributions they do provide some insight into selecting a projection for reconciliation.  If the value of $\hat{\bm \mu}$ were equi-probable in all directions then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for ${\bm R}$ since it would in some sense represent a `median' direction for ${\bm \mu}-\hat{\bm \mu}$.  However, the one step ahead in-sample errors are usually correlated suggesting that $\hat{\bm \mu}$ is more likely to fall in some directions than others.  As such an orthogonal projection after transformation by the inverse of the one step ahead in-sample errors may be more intuitively appealing.  This is exactly what the MinT projection estimates, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
